Collaboration in Ad Hoc Teamwork: \\ Ambiguous Tasks, Roles, and Communication

### 2016-03-17 paper/conclusion.tex
integrating Manuel comments
paper ready for final publication

\section{Conclusions}

@@

But considering that many hypotheses is costly, and the approach presented in this paper computationally expensive (see Figure~\ref{fig:comptime}). An important challenge for the future is to find ways to approximate this process while minimizing the impact on the performance of the team. A potential avenue is to consider a sampling strategy, evaluating only a subset of all possible domains each step.

>>>>

\vspace{1em} % so conclusion section header is not at the bottom of the page
\section{Conclusions}

@@

But considering that many hypotheses is costly, and the approach presented in this paper is computationally expensive (see Figure~\ref{fig:comptime}). An important challenge for the future is to find ways to approximate this process while minimizing the impact on the performance of the team. A potential avenue is to consider a sampling strategy, evaluating only a subset of all possible domains each step.

### 2016-03-17 paper/introduction.tex
paper ready for final publication

A similar problem, where both the task and the communication are unknown, has been investigated in human-machine interaction \cite{grizou2014interactive}. They consider only two agents, a teacher and a learner. Their learning agent can only act on its own towards the success of the task and can observe non-symbolic communication signals from the teaching agent, whose meaning is part of a finite set but initially unknown. This work differs mainly by the multiagent scenario. On the one hand, it makes the problem less tractable, but on the other hand, it simplifies the problem because the learning agent has access to more information (i.e. it can observe other agent's actions).

>>>>

A similar problem, where both the task and the communication are unknown, has been investigated in human-machine interaction \cite{grizou2013robot,grizou2014interactive}. They consider only two agents, a teacher and a learner. Their learning agent can only act on its own towards the success of the task and can observe non-symbolic communication signals from the teaching agent, whose meaning is part of a finite set but initially unknown. This work differs mainly by the multiagent scenario. On the one hand, it makes the problem less tractable, but on the other hand, it simplifies the problem because the learning agent has access to more information (i.e. it can observe other agent's actions).
